# Wearable Computing / Peer Assessments / Getting and Cleaning Data Course Project


**Chris Thatcher, February 21, 2015**

*This code book documents the steps we took to tidy the publicly available data set
described by this assignment.*

Here is the assignment requirments verbatim:

1. Merges the training and the test sets to create one data set.
1. Extracts only the measurements on the mean and standard deviation for each measurement. 
1. Uses descriptive activity names to name the activities in the data set
1. Appropriately labels the data set with descriptive variable names. 
1. From the data set in step 4, creates a second, independent tidy data set with the average of each variable for each activity and each subject.

## Resulting Tidy Data Set

```{r}
library(data.table)

average_activity_values = fread('tidy_final.txt')
```

The final tidy data set contains ```r length(names(average_activity_values))``` variables,
one identifying the subject, **subject**, one identifying the activity, **activity**,
and the remaining variables are the averages, aggregated by subject and activity,
of the mean and standard deviations as recorded in the original data set.

Additional information about how the data was original collected is available inside
the data source zip https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip
and at http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones.

## A Summary of the columns

There are no NA values in any columns.

```{r}
summary(average_activity_values)
```

## All variables and their types.

Aside from **subject** and **activity** which are integer and factor respectivly,
all other columns are numeric.

```{r}
str(average_activity_values)
```


